Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-11-05 draft.tex
typo
strict

Given a filtered associative algebra whose associated graded is commutative, there exists a Poisson bracket on the associated graded algebra. 
If the associated graded of a filtered $\EE_n$ algebra is commutative, then it carries the structure of a $\PP_n$ algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$. 
There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, introduced by Safronov \cite{Pavel1, Pavel2}, whose definition we recall below.

\begin{prp} 
\label{prp:poisson}
The associated graded pair $({\rm Gr} \; \fZ_n(\fg) , {\rm Gr} \; \UU_n(\fg))$ determines an algebra over the operad $\PP_{[n+1,n]}$. 
\end{prp}

@@

The associated graded factorization algebras ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ are equipped with Poisson brackets that are compatible with the factorization structure.

For $k \geq -1$, a {\em $\PP_k$-factorization algebra} is a factorization algebra $\bA$ such that for every open set $U$ the cochain complex $\bA(U)$ is equipped with the structure of a $\PP_k$ algebra. 
Furthermore, we require that the factorization structure maps be compatible with the $\PP_k$ algebra structure.

Theorem \ref{thm:lurie1} combines with the additivity result of \cite{SafronovAdd} to show that there is an equivalence of categories between the category of locally constant $\PP_k$-factorization algebras on $\RR^n$ and $\PP_{n+k}$ algebras.

In light of this, the following lemma implies that ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ determine $\PP_n$ and $\PP_{n+1}$ algebras respectively.

@@

\begin{proof}
For any $L_\infty$ algebra $\fh$, the associated graded of the Chevalley--Eilenberg complex ${\rm Gr} \; \cliels {\rm Sym} (\fh [1])$ is equipped with the structure of a $\PP_0$ algebra.
It is given by the sum of the $L_\infty$-operations $\ell_2 + \ell_3 + \cdots$. 
This observation implies that ${\rm Gr} \; \bU_n (\fg)$ is a $\PP_0$-factorization algebra.

@@

The pair $(\fZ_n(\fg), \UU_n(\fg))$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
At the level of the associated graded algebras, 
we obtain an algebra over a certain classical limit of this operad that takes into account the aforementioned Poisson structures.
The definition of this two-colored operad $\PP_{[n+1,n]}$ can be found in~\cite{SafronovCoiso}. 
A {\em $\PP_{[n+1,n]}$ algebra} consists of a pair $(A,B)$ where $A$ is a $\PP_{n+1}$ algebra and $B$ is a $\PP_n$ algebra that receives an action by $A$.

The action of $\bZ_n(\fg)$ on $\bU_n(\fg)$ descends to an action at the level of the associated graded factorization algebras
Together with Lemma~\ref{lmm:pois1}, we obtain Proposition~\ref{prp:poisson}.

@@

  Now, there is a natural inclusion of cochain complexes of the smooth (non-distributional) compactly supported de Rham forms inside of the distributional ones:
  \begin{equation}\label{eqn:AB}
    \Omega_c^\bu(V \times [0,\epsilon) \, | \, V) \otimes \fg[2]\Bar{\Omega}_c^\bu(V \times [0,\epsilon) \, | \, V) \otimes \fg[2] .
  \end{equation}
  Furthermore, using ellipticity of the de Rham operator we can assert by the Atiyah--Bott lemma \cite{??} that this inclusion is a quasi-isomorphism.

>>>>

Given a filtered associative algebra whose associated graded is commutative, there exists a Poisson bracket on the associated graded algebra. 
If the associated graded of a filtered $\EE_n$ algebra is commutative, then it carries the structure of a $\PP_n$ algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$.
In particular, ${\rm Gr} \; \UU_n (\fg)$ has the structure of a $\PP_n$-algebra.

There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, introduced by Safronov \cite{Pavel1, Pavel2}.
Using our model, we will see that the pair $({\rm Gr} \; \fZ_n (\fg), {\rm Gr} \; \UU_n(\fg))$ is an algebra over this two-colored operad.
In particular, this implies that ${\rm Gr} \; \fZ_n (\fg)$ carries the structure of a $\PP_{n+1}$-algebra which ``acts'' on the $\PP_n$-algebra ${\rm Gr} \; \UU_n(\fg)$.

%\begin{prp}
%\label{prp:poisson}
%The associated graded pair $({\rm Gr} \; \fZ_n(\fg) , {\rm Gr} \; \UU_n(\fg))$ determines an algebra over the operad $\PP_{[n+1,n]}$.
%\end{prp}

@@

The associated graded factorization algebras ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ are equipped with Poisson brackets that are compatible with the factorization structure. 
For the remainder of this section we will assume that $\fg$ is a strict dg Lie algebra so that we can work with strict Poisson brackets
in the category of dg algebras.

\begin{dfn}
  A $\PP_m$-algebra is a commutative dg algebra $A$ equipped with a bracket
  \[
    \{\cdot , \cdot\} : A \otimes_k A \to A
  \]
  which defines a graded Lie bracket on $A[m-1]$ and satisfies the graded Leibniz rule
  \[
    \{a, b \cdot c\} = \{a,b\} \cdot c + (-1)^{|b||c|} \{a , c\} \cdot b .
  \]
\end{dfn}

A {\em $\PP_m$-factorization algebra} is a factorization algebra $\bA$ such that for every open set $U$ the cochain complex $\bA(U)$ is equipped with the structure of a $\PP_m$ algebra and that the factorization structure maps are compatible with the $\PP_m$-algebra structures.
In particular, we note that a $\PP_m$-factorization algebra is a commutative factorization algebra.

There is an additivity theorem of Dunn and Lurie for $\EE_n$-algebras, see Theorem ?? in \cite{LurieHA}, which states an equivalence of $\infty$-categories between the category of $\EE_{n+1}$-algebras and the category of algebras in $\EE_{n}$-algebras.
Safronov \cite{SafronovAdd} has proven a Poisson version of this result which states that there is an equivalence of $\infty$-categories between the category of $\PP_{n+1}$ algebras and the category of algebras in $\PP_{n}$-algebras.

In light of this result, the following lemma implies that ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ determine $\PP_n$ and $\PP_{n+1}$ algebras respectively.

@@

\begin{proof}
For any Lie algebra $\fh$, the associated graded of the Chevalley--Eilenberg complex ${\rm Gr} \; \cliels {\rm Sym} (\fh [1])$ is equipped with the structure of a $\PP_0$ algebra with $\PP_0$-bracket determined by the Lie bracket on $\fh$.
This observation implies that ${\rm Gr} \; \bU_n (\fg)$ is a $\PP_0$-factorization algebra.

@@

The pair $(\fZ_n(\fg), \UU_n(\fg))$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
At the level of the associated graded algebras, 
we obtain an algebra over a certain classical limit of this operad that takes into account the aforementioned Poisson structures.
The definition of this two-colored operad $\PP_{[n+1,n]}$ can be found in~\cite{SafronovCoiso}. 
Roughly speaking, a {\em $\PP_{[n+1,n]}$ algebra} consists of a pair $(A,B)$ where $A$ is a $\PP_{n+1}$ algebra and $B$ is a $\PP_n$ algebra that receives an action by $A$.

The action of $\bZ_n(\fg)$ on $\bU_n(\fg)$ descends to an action at the level of the associated graded factorization algebras
Together with Lemma~\ref{lmm:pois1}, we see that the associated graded pair is an algebra over $\PP_{[n+1,n]}$.

@@

  Now, there is a natural inclusion of cochain complexes of the smooth (non-distributional) compactly supported de Rham forms inside of the distributional ones:
  \begin{equation}\label{eqn:AB}
    \Omega_c^\bu(V \times [0,\epsilon) \, | \, V) \otimes \fg[2] \hookrightarrow \Bar{\Omega}_c^\bu(V \times [0,\epsilon) \, | \, V) \otimes \fg[2] .
  \end{equation}
  Furthermore, using ellipticity of the de Rham operator we can assert by the Atiyah--Bott lemma \cite{??} that this inclusion is a quasi-isomorphism.
